Bayesian Hierarchical Models for Common Components across Multiple System Configurations

### 2017-10-26 paperDraft3.tex
working on edits

\subsection{Modeling Reliability}
A standard reliability analysis employed by the Department of Defense (DoD) test
community considers each test phase independently and uses the exponential
distribution to model the miles between failure ~\cite{ref1}. The traditional
analysis is overly simplistic, relies on correct modeling assumptions
and ignores valuable information learned about the individual vehicles and their
failure modes.

@@

>>>>

\subsection{Modeling Reliability}
A standard reliability analysis employed by the Department of Defense (DoD) test
community considers each test phase independently and uses the exponential
distribution to model the miles between failure for the system ~\cite{ref1}. The
traditional analysis is overly simplistic, relies on correct modeling
assumptions and ignores valuable information learned about the individual
vehicles and their failure modes.

@@

In this reliability setting we are analysing time to failure data measured in
miles for a multiple component system with the primary interest in the system
failure rate and future failure counts.  The most common models used in this
failure rate analysis are lifetime distributions and the most common for failure
count analysis is the \emph{Poisson process} counting model.  We will utilize
both and the relationships between them.

The methodology section is organized as follows... section 3.1...
